\chapter{Introduction}

\section{Purpose}

The purpose of the MLUD is to digitize and streamline the process of cataloging and monitoring the used schoolbook market held at Lokalino during the summer. The system aims to eeduce the workload on operators, particularly for repetitive tasks, minimize errors by eliminating manual transcription processes and significantly decrease paper usage.

\section{Scope}

The MLUD will be used by operators, providers and buyers. The system will allow operators to manage the catalog of books, providers to add books to the catalog and buyers to search for books. The system will also allow operators to account for the books sold and help the financial transactions between providers and buyers.
The system does not handle actual financial transactions but keeps a record of the money involved in the transactions.

\noindent The boundaries of the system are as follows:
\begin{itemize}
    \item Operations are limited to the Lokalino summer book market.
    \item The platform will only retain data for one year after market closure, except for users who opt into the mailing list.
\end{itemize}

\section{Definitions, acronyms and abbreviations}

\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Term}   & \textbf{Definition}             & \textbf{Acronym} \\ \hline
        Operator        & A Lokalino employee             & OP               \\
        Provider        & A person who has books to sell  & PR               \\
        Buyer           & A person who wants to buy books & BY               \\
        Mercatino Libri & The system                      & MLUD             \\\hline
    \end{tabular}
\end{table}